---
title: "Student Spending"
subtitle: 
author: " Brainless Data Group <br> Alfred, Leo, Rolan, Yuki, Ariana"
institute: "University of Edinburgh"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(tidyverse)
library(palmerpenguins)
library(knitr)
library(xaringanthemer)
library(tidymodels)
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r load-data, include=FALSE}
# Read data and replace all empty space in the survey responds with NA
monthly_expense <- read.csv("monthly_expense.csv", na = "")

```

```{r include=FALSE}
style_xaringan(
  title_slide_background_image = "wallpaper.jpg",
  title_slide_text_color = "black")

```

class: center, middle

## What Affects Student Spending?

---
class: inverse, center, middle

# Kaggle

---
class: inverse, center, middle

# Variables - 13

---
class: inverse, center, middle

## Observations - 105

---
# Variables that we will use...

.pull-left[
# Monthly Expense
]
.pull-right[
- Gender
- Year of Study
- Living
- Scholarship
- Part-time
- Transport
- Smoking
- Drinking
- Games and Hobbies
- Self-care
- Monthly Subscription
]

---
# Table

```{r table, echo = FALSE}
glimpse(monthly_expense)

```

---
class: center, middle
# Hypothesis

 Entertainment has the most effect on students' monthly expense.
---
```{r, summarise, echo = FALSE}
# Create function that will plot counts against different responds on one variable

#################### 
me <- read.csv("monthly_expense.csv", na = "")%>% filter(!is.na(Monthly_expenses))
####################

x <- function(i){
ggplot(data = me[i], aes(x = names(me[i]))) +
  geom_bar() +
  facet_wrap(names(me[i])) +
    labs(x = names(me[i]))
  
}

```

## Counts for variables
.pull-left[
```{r, echo= FALSE}
x(1)
x(2)
```
]

.pull-right[
```{r, echo= FALSE}
x(3)
x(4)
```
]
---

## Counts for variables
.pull-left[
```{r, echo= FALSE}
x(5)
x(6)
```
]

.pull-right[
```{r, echo= FALSE}
x(7)
x(8)
```
]
---
## Counts for variables
.pull-left[
```{r, echo= FALSE}
x(9)
x(10)
```
]

.pull-right[
```{r, echo= FALSE}
x(11)
x(12)
```
]
---
# Linear regression 
```{r reg 1-st_try, echo = FALSE}
reg_try <- linear_reg() %>%
  set_engine("lm") %>%
  fit(Monthly_expenses ~., data = me) 
REG_TRY <-reg_try %>% tidy()
REG_TRY

#adj.r.squared
glance(reg_try)$adj.r.squared
```
---
##Variable: Gender - Cosmetics_._Self.care
```{r bad_variables1, echo = FALSE}
# First of all consider counts:counts for drinking and smoking have mostly negative responds, so we neglect those variables

#According to reg_try Cosmetics_._Self.care  has weak correlation to the monthly expenses, so we check its graph against monthly expenses. If we also consider gender for this graph, we get that most of females do use cosmetics and most of males do not. So Cosmetics_._Self.care is highly dependent on Gender and we can neglect this variable as well. 


ggplot(data = me, aes(x = Cosmetics_._Self.care)) +
    geom_bar() + facet_wrap(~Gender) +
  labs(title = "Cosmetics_._Self.care and Gender")
######################################################
```

---
##Games_._Hobbies- Monthly_Subscriptions
.pull-left[
```{r bad_variables2, echo= FALSE}
#In second linear regression attempt variables: Drinks, Smoking, Cosmetics_._Self.care were deleted (adj.r.squared ~ 0.40). For this attempt data splitting for regression training was used. According to this attempt Games_._Hobbies, Scholarship are negligible, so we plot their graphs against monthly expenses. Yet, their graphs demonstrate some correlation, so we try to plot Scholarship and Games_._Hobbies against other variables.


#We can observe some similar patterns for the graphs of Monthly_Subscription(Yes) and Games_._Hobbies(Yes). Therefore, for the third linear regression we will exclude one of those: Monthly_Subscriptions.

ggplot(data = filter(me, !is.na(Monthly_Subscription)), aes(x = Monthly_expenses)) +
  geom_bar() +
  facet_wrap(~ Monthly_Subscription) +
  labs(title = "Monthly_Subscription")
```
]
.pull-right[
```{r, echo= FALSE}
ggplot(data = me, aes(x = Monthly_expenses)) +
  geom_bar() +
  facet_wrap(~ Games_._Hobbies) +
  labs(title = "Games_._Hobbies")

```
]

---
```{r reg, echo= FALSE} 
set.seed(1000)
me_split <- initial_split(me, prop = 0.8)

train_data <- training(me_split)
testing_data <- testing(me_split)


# Second linear regression
reg <- linear_reg() %>%
  set_engine("lm") %>%
  fit(Monthly_expenses ~ .  - Drinks - Smoking - Cosmetics_._Self.care,data = train_data) 
reg_predict <- predict(reg, testing_data) %>%
  bind_cols(testing_data) %>% transmute(resid = .pred - Monthly_expenses, Monthly_expenses = Monthly_expenses, .pred = .pred)
REG <- reg%>%tidy()
```

---
# Gender

```{r, Gender, echo = FALSE}
me <- monthly_expense %>%
  filter(!is.na(Monthly_expenses))

ggplot(data = me, mapping = aes(x = Monthly_expenses, y = Gender, fill = Gender)) +
  geom_boxplot(show.legend = FALSE) +
  labs(x = "Mothly Expenses",
       y = "Gender", 
       title = "Gender vs Monthly Expense")
```

---
# Age

```{r, Age, echo=FALSE}
me <- monthly_expense %>%
  filter(Monthly_expenses < 600) %>%
  mutate(Age = as.character(Age))
ggplot(data = me, mapping = aes(y = Age, 
                                x = Monthly_expenses,
                                fill = Age)) + 
  geom_boxplot() +
  labs(title = "Monthly Expenses",
       y = "Age vs Monthly Expenses")
```

---
# Year of Study

``` {r, Study Year, echo = FALSE}
me <- monthly_expense %>%
  filter(Monthly_expenses < 600,
         Study_year <= 4) %>%
  mutate(Study_year = as.character(Study_year))
ggplot(data = me, mapping = aes(y = Monthly_expenses,
                                x = Study_year,
                                fill = Study_year)) +
  geom_violin(show.legend = FALSE)  +
  labs(title = "Study year vs Monthly Expenses",
       x = "Study Year",
       y = "Monthly Expenses")
```

---
# Age and Study Year

```{r, echo=FALSE}
me <- monthly_expense %>%
  mutate(Study_year = as.factor(Study_year)) %>%
  filter(!is.na(Age) & !is.na(Study_year))

ggplot(data = me, mapping = aes(x = Age,
                                fill = Study_year)) +
  geom_bar()

```

---
#Living

```{r, Living, echo = FALSE}
me <- monthly_expense %>%
  mutate(Living = as.factor(Living)) %>%
  filter(!is.na(Living) & !is.na(Monthly_expenses))
  ggplot(data = me, mapping = aes(x = Monthly_expenses, y = Living, fill = Living)) +
geom_boxplot(show.legend = FALSE) +
    labs(title = "Types of Living vs Monthly Expenses",
         x = "Monthly Expenses",
         y = "Living")

```

---
#Scholarship

```{r, Scholarship, echo = FALSE}
me <- monthly_expense %>%
  filter(!is.na(Scholarship) & !is.na(Monthly_expenses))

ggplot(data = me, mapping = aes(x = Monthly_expenses, 
                     y = Scholarship, 
                     fill = Scholarship)) +
  geom_boxplot(show.legend = FALSE) +
  labs(title = "Scholarship vs Monthly Expenses",
       x = "Monthly Expenses",
       y = "Scholarship")
```

---
# Part time job

``` {r, Part time job, echo = FALSE}
me <- monthly_expense %>%
  filter(!is.na(Part_time_job) & !is.na(Monthly_expenses))
ggplot(data = me, mapping = aes(x = Monthly_expenses,
                                y = Part_time_job,
                                fill = Part_time_job)) +
  geom_boxplot(show.legend = FALSE) +
  labs(title = "Part-time Job vs Monthly Expenses",
       x = "Monthly Expenses",
       y = "Part-Time Job")

```

---
# Transportation 

``` {r, Transportation, echo = FALSE}
me <- monthly_expense %>%
  filter(!is.na(Transporting) & !is.na(Monthly_expenses))
ggplot(data = me, mapping = aes(x = Monthly_expenses,
                                y = Transporting,
                                fill = Transporting)) +
  geom_boxplot(show.legend = FALSE) +
  labs(title = "Transportation vs Monthly Expenses",
       x = "Monthly Expenses",
       y = "Transportation")

```

---
# Game and Hobbies

```{r, Game and Hobbies, echo = FALSE}
me <- monthly_expense %>%
  filter(!is.na(Games_._Hobbies) & !is.na(Monthly_expenses))

ggplot(data = me, mapping = aes(x = Monthly_expenses, y = Games_._Hobbies, fill = Games_._Hobbies))+
    geom_boxplot()+
    labs(x = "Monthly Expenses",
         y = "Games & Hobbies", 
         title = "The Relationship Between Games & Hobbies and Monthly Expenses")
```

---


