---
title: "Student Spending"
subtitle: 
author: " Brainless Data Group <br> Alfred, Leo, Rolan, Yuki, Ariana"
institute: "University of Edinburgh"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(tidyverse)
library(palmerpenguins)
library(knitr)
library(xaringanthemer)
library(tidymodels)
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r load-data, include=FALSE}
# Read data and replace all empty space in the survey responds with NA
monthly_expense <- read.csv("monthly_expense.csv", na = "")

```

```{r include=FALSE}
style_xaringan(
  title_slide_background_image = "wallpaper.jpg",
  title_slide_text_color = "black")

```

class: center, middle

## What Affects Student Spending?

---
class: inverse, center, middle

# Kaggle

---
class: inverse, center, middle

# Variables - 13

---
class: inverse, center, middle

## Observations - 105

---
# Variables that we will use...

.pull-left[
# Monthly Expense
]
.pull-right[
- Gender
- Year of Study
- Living
- Scholarship
- Part-time
- Transport
- Smoking
- Drinking
- Games and Hobbies
- Self-care
- Monthly Subscription
]

---
# Table

```{r table, echo = FALSE}
glimpse(monthly_expense)

```

---
class: center, middle
# Hypothesis

 Entertainment has the most effect on students' monthly expense.

---
# Gender

```{r, Gender, echo = FALSE}
me <- monthly_expense %>%
  filter(!is.na(Monthly_expenses))

ggplot(data = me, mapping = aes(x = Monthly_expenses, y = Gender, fill = Gender)) +
  geom_boxplot(show.legend = FALSE) +
  labs(x = "Mothly Expenses",
       y = "Gender", 
       title = "Gender vs Monthly Expense")
```

---
# Age

```{r, Age, echo=FALSE}
me <- monthly_expense %>%
  filter(Monthly_expenses < 600) %>%
  mutate(Age = as.character(Age))
ggplot(data = me, mapping = aes(y = Monthly_expenses, 
                                x = Age,
                                fill = Age)) + 
  geom_boxplot() +
  labs(title = "Age vs Monthly Expenses",
       y = "Monthly Expenses")
```

---
# Year of Study

``` {r, Study Year, echo = FALSE}
me <- monthly_expense %>%
  filter(Monthly_expenses < 600,
         Study_year <= 4) %>%
  mutate(Study_year = as.character(Study_year))
ggplot(data = me, mapping = aes(y = Monthly_expenses,
                                x = Study_year,
                                fill = Study_year)) +
  geom_violin(show.legend = FALSE)  +
  labs(title = "Study year vs Monthly Expenses",
       x = "Study Year",
       y = "Monthly Expenses")
```

---
#Living

```{r, Living, echo = FALSE}
me <- monthly_expense %>%
  mutate(Living = as.factor(Living)) %>%
  filter(!is.na(Living) & !is.na(Monthly_expenses))
  ggplot(data = me, mapping = aes(x = Living,y = Monthly_expenses, fill = Living)) +
geom_boxplot(show.legend = FALSE) +
    labs(title = "Types of Living vs Monthly Expenses",
         x = "Living",
         y = "Monthly Expenses")

```

---
#Scholarship

```{r, Scholarship, echo = FALSE}
me <- monthly_expense %>%
  filter(!is.na(Scholarship) & !is.na(Monthly_expenses))

ggplot(data = me, mapping = aes(x = Scholarship, 
                     y = Monthly_expenses, 
                     fill = Scholarship)) +
  geom_boxplot(show.legend = FALSE) +
  labs(title = "Scholarship vs Monthly Expenses",
       x = "Scholarship",
       y = "Monthly Expenses")
```

---
# Part time job

``` {r, Part time job, echo = FALSE}
me <- monthly_expense %>%
  filter(!is.na(Part_time_job) & !is.na(Monthly_expenses))
ggplot(data = me, mapping = aes(x = Part_time_job,
                                y = Monthly_expenses,
                                fill = Part_time_job)) +
  geom_boxplot(show.legend = FALSE) +
  labs(title = "Part-time Job vs Monthly Expenses",
       x = "Part-Time Job",
       y = "Monthly Expenses")

```

---
# Transportation 

``` {r, Transportation, echo = FALSE}
me <- monthly_expense %>%
  filter(!is.na(Transporting) & !is.na(Monthly_expenses))
ggplot(data = me, mapping = aes(x = Transporting,
                                y = Monthly_expenses,
                                fill = Transporting)) +
  geom_boxplot(show.legend = FALSE) +
  labs(title = "Transportation vs Monthly Expenses",
       x = "Transportation",
       y = "Monthly Expenses")

```

---
# Game and Hobbies

```{r, Game and Hobbies, echo = FALSE}
me <- monthly_expense %>%
  filter(!is.na(Games_._Hobbies) & !is.na(Monthly_expenses))

ggplot(data = me, mapping = aes(x = Games_._Hobbies, y = Monthly_expenses, fill = Games_._Hobbies))+
    geom_boxplot()+
    labs(x = "Games & Hobbies" ,
         y = "Monthly expenses", 
         title = "The Relationship Between Games & Hobbies and Monthly Expense")
```